Automatic Amortized Analysis for Imperative Code

### 2014-05-23 paper/main.tex
some more notes

@@

\begin{itemize}
\item have formal soundness proof with respect to cost semantics
\item can deal with resources that \emph{become available} (e.g, freeing memory) in an execution
\item derive global bounds for the program as a function of the inputs (as opposed to local loop bounds)
\item can handle advance control flow such as break, return, mutual recursive functions
\item do not rely on abstract-interpretation based invariant generation
\item show that constant factors are very precise with respect to the cost semantics
\item demonstrate that the analysis is applicable in the formal verification of system code
\end{itemize}

>>>>

\paragraph{to do}

\begin{itemize}
\item describe schedulability analysis for two schedulers
\item include program logic from the stack paper for arbitrary resources
\item what operational semantics to use? 
\item verify automatic tool with program logic
\item derive some crazy bounds (polynomial? logarithmic?) with the logic
\item logic can also be used by automation: put linear constraints in the precondition
\end{itemize}

@@

\begin{itemize}
\item integrates well with hand-derived bounds in a program logic
\item have formal soundness proof with respect to cost semantics
\item can attach certificate to the code (proof-carrying code)
\item can deal with resources that \emph{become available} (e.g, freeing memory) in an execution
\item derive global bounds for the program as a function of the inputs (as opposed to local loop bounds)
\item can handle advance control flow such as break, return, mutual recursive functions
\item do not rely on abstract-interpretation based invariant generation
\item show that constant factors are very precise with respect to the cost semantics
\item demonstrate that the analysis is applicable in the formal verification of system code
\end{itemize}
